Interactions with Domain Experts

### 2021-01-17 StateOfPractice/Methodology/Interactions with Domain Experts.tex
updated Research Proposal

>>>>

\subsubsection{State of the Practice}

MEng students will perform assessments to the state of the practice in several
Scientific Computing Software (SCS) domains. Domain analysis will be conducted
(related to Section \ref{domain_analysis}). About 20 to 30 software projects
will be chosen for the measurements, and the software list is in Section
\ref{software_list}. The questions and metrics (including empirical
measurements) to assess the projects are documented in the Section
\ref{measurement_template}.

Additionally, we will also perform Usability Tests (Section
\ref{usability_tests}) and Modifiability Experiment (Section
\ref{modifiability_experiment})

To compare each software quality and the overall quality, we will use the
Analytic Hierarchy Process (AHP) to rank software projects in each domain. The
first ranking will be for all projects, and the final ranking will be for the
short list projects (more details in Section \ref{survey_short_list_projects}).
The ranking results will be the topic for our last meeting - the concluding
meeting in Section \ref{concluding_meeting}.

\subsubsection{Impact of MDE on the Sustainability of SCS}
